quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-04 paper-quollr.Rmd
Updated the intro

This paper presents the R package, `quollr` which introduce a new visual tool in determining which NLDR technique and which (hyper)parameter choice gives most accurate representation of high-dimensional data. The methodology of the algorithm is explained in *cite the methodology paper*. Furthermore, the `quollr` package enables users to perform hexagonal binning [@dan2023], resulting in the generation of regular hexagons. The software is available from the Comprehensive R Archive Network (CARN) at [https://CRAN.R-project.org/package=quollr](https://CRAN.R-project.org/package=quollr).

>>>>

This paper presents the R package, `quollr` which introduce a new visual tool in determining which Non-linear dimension reduction (NLDR) technique and which (hyper)parameter choice gives most accurate representation of high-dimensional data. The methodology of the algorithm is explained in *cite the methodology paper*. Furthermore, the `quollr` package enables users to perform hexagonal binning [@dan2023], resulting in the generation of regular hexagons. The software is available from the Comprehensive R Archive Network (CARN) at [https://CRAN.R-project.org/package=quollr](https://CRAN.R-project.org/package=quollr).
